A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-11-02 bioc-workflow.Rnw
interactive vis section

\begin{figure}[!ht]
  \centering
<<plotDist, out.width=".65\\textwidth">>=
hlo <- hl[, order(hl$Iodixonal.Density)]
plotDist(hlo[fData(hlo)$markers == "Mitochondrion", ],
         pcol = "purple", fractions = "Fraction.No")
title(main = "Marker occupancy profiles along the gradient")
matlines(t(exprs(hlo[fData(hlo)$markers == "Peroxisome", ])),
         lty = 1, col = "darkblue", type = "l")
legend("topleft", c("Mitochondrion", "Peroxisome"),
       lty = 1, col = c("purple", "blue"), bty = "n")
@  
  \caption{Mitochondrion and peroxisome protein profiles.}
  \label{fig:plotDist2}
\end{figure}

@@

@@

Visualisation and data exploration is an important aspect of data
analyses allowing one to shed light on data structure and patterns of
interest. Using the \Biocpkg{pRolocGUI} package we can
interactively visualise, explore and interrogate quantitative spatial
proteomics data. The \Biocpkg{pRolocGUI} package is currently
under active development and it relies on the \texttt{shiny} framework for
reactivity and interactivity. The package currently distributes 3
different GUI's ("main" (default), "compare" or "compare") which are
wrapped and launched by the \texttt{pRolocVis} function. In the below code
chunk we lauch the main app (note, we do not need to specify the
argument, \texttt{app = "main"} as it is the default).

@@

As diplayed in the screenshot above, the "main" application is
designed for exploratory data analysis and is divied into 3 tabs: (1)
PCA, (2) Profiles and (3) Table selection. The default view upon
loading is the PCA tab, which features a clickable interface and
zoomable PCA plot with an interactive data table for displaying the
quantitation information. Particular proteins of interest can be
highlighted using the text search box. There is also an alternate
profiles tab for visualisation of the protein profiles, which can be
used to examine the patterns of proteins of interest. The Table
selection tab provides an interface to control data table column
selection.

@@

<<compareapp, eval = FALSE, echo = TRUE>>=
data(hyperLOPIT2015ms3r1)
data(hyperLOPIT2015ms3r2)
mydata <- MSnSetList(list(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2))
pRolocVis(mydata, app = "compare")
@

@@

The comparison app loads the two PCA plots side-by-side. Only common
proteins between the two data sets are displayed. As per the main
application proteins can be searched, identified and highlighted on
both PCA plots and in the dedicated profiles tab. One key feature of
the compare application is the ability to re-map the second dataset
onto the PCA data space of the first (reference) data set (see
\texttt{?pRolocVis} and the argument \texttt{remap = TRUE}). Using the first dataset
as the reference set, PCA is carried out on the first dataset and the
standard deviations of the principal components (i.e. the square roots
of the eigenvalues of the covariance/correlation matrix) and the
matrix of variable loadings (i.e. a matrix whose columns contain the
eigenvectors) are stored and then used to calculate the principal
components of the second dataset. Both datasets are scaled and
centered in the usual way. The first dataset appears on the left, and
the second re-mapped data appears on the right. The order of the first
(the reference data for remapping) and second dataset can be changed
through regeneration/re-ordering of the \texttt{MSnSetList} object.

The final application "classify", has been designed to view machine
learning classification results according to user-specified thresholds
for the assignment of proteins to its sub-cellular location, this is
discussed later in the subsection \textit{thresholding} in the
\textit{supervised machine learning section}.

>>>>

\begin{figure}[!ht]
  \centering
<<plotDist, out.width=".6\\textwidth", fig.asp=1/3>>=
hlo <- hl[, order(hl$Iodixonal.Density)]
plotDist(hlo[fData(hlo)$markers == "Mitochondrion", ],
         pcol = "purple", fractions = "Fraction.No")
title(main = "Marker occupancy profiles along the gradient")
matlines(t(exprs(hlo[fData(hlo)$markers == "Peroxisome", ])),
         lty = 1, col = "darkblue", type = "l")
legend("topleft", c("Mitochondrion", "Peroxisome"),
       lty = 1, col = c("purple", "blue"), bty = "n")
@  
  \caption{Mitochondrion and peroxisome protein profiles.}
  \label{fig:plotDist2}
\end{figure}

@@

\clearpage

@@

Visualisation and data exploration is an important aspect of data
analyses allowing one to shed light on data structure and patterns of
interest. Using the \Biocpkg{pRolocGUI} package we can interactively
visualise, explore and interrogate quantitative spatial proteomics
data. The \Biocpkg{pRolocGUI} package is currently under active
development and it relies on the \texttt{shiny} framework for
reactivity and interactivity. The package currently distributes 3
different GUI's (\textit{main} (default), \textit{compare} or
\textit{compare}) which are wrapped and launched by the
\texttt{pRolocVis} function. In the below code chunk we lauch the main
app (note, we do not need to specify the argument, \texttt{app =
  "main"} as it is the default).

@@

As diplayed in the screenshot above, the \textit{main} application is
designed for exploratory data analysis and is divied into 3 tabs: (1)
PCA, (2) Profiles and (3) Table selection. The default view upon
loading is the PCA tab, which features a clickable interface and
zoomable PCA plot with an interactive data table for displaying the
quantitation information. Particular proteins of interest can be
highlighted using the text search box. There is also an alternate
profiles tab for visualisation of the protein profiles, which can be
used to examine the patterns of proteins of interest. The Table
selection tab provides an interface to control data table column
selection.

@@

<<compareapp, eval = FALSE, echo = TRUE>>=
data(hyperLOPIT2015ms3r1)
data(hyperLOPIT2015ms3r2)
hllst <- MSnSetList(list(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2))
pRolocVis(hllst, app = "compare")
@

@@

The comparison app loads the two PCA plots side-by-side. Only common
proteins between the two data sets are displayed. As per the main
application, proteins can be searched, identified and highlighted on
both PCA plots and in the dedicated profiles tab. One key feature of
the compare application is the ability to re-map the second dataset
onto the PCA data space of the first (reference) data set (see
\texttt{?pRolocVis} and the argument \texttt{remap = TRUE}). Using the first dataset
as the reference set, PCA is carried out on the first dataset and the
standard deviations of the principal components (i.e. the square roots
of the eigenvalues of the covariance/correlation matrix) and the
matrix of variable loadings (i.e. a matrix whose columns contain the
eigenvectors) are stored and then used to calculate the principal
components of the second dataset. Both datasets are scaled and
centered in the usual way. The first dataset appears on the left, and
the second re-mapped data appears on the right. The order of the first
(the reference data for remapping) and second dataset can be changed
through regeneration/re-ordering of the \texttt{MSnSetList} object.

The final application \textit{classify}, has been designed to view
machine learning classification results according to user-specified
thresholds for the assignment of proteins to its sub-cellular
location, as discussed later in the subsection \textit{thresholding}
in the \textit{supervised machine learning section}.

### 2016-11-02 bioc-workflow.tex
interactive vis section

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Wed Nov  2 14:41:44 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Wed Nov  2 14:41:44 2016 
## Subset [6725,20][5032,20] Wed Nov  2 14:41:44 2016 
## Removed features with more than 0 NAs: Wed Nov  2 14:41:44 2016 
## Dropped featureData's levels Wed Nov  2 14:41:44 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hlo} \hlkwb{<-} \hlstd{hl[,} \hlkwd{order}\hlstd{(hl}\hlopt{$}\hlstd{Iodixonal.Density)]}
\hlkwd{plotDist}\hlstd{(hlo[}\hlkwd{fData}\hlstd{(hlo)}\hlopt{$}\hlstd{markers} \hlopt{==} \hlstr{"Mitochondrion"}\hlstd{, ],}
         \hlkwc{pcol} \hlstd{=} \hlstr{"purple"}\hlstd{,} \hlkwc{fractions} \hlstd{=} \hlstr{"Fraction.No"}\hlstd{)}
\hlkwd{title}\hlstd{(}\hlkwc{main} \hlstd{=} \hlstr{"Marker occupancy profiles along the gradient"}\hlstd{)}
\hlkwd{matlines}\hlstd{(}\hlkwd{t}\hlstd{(}\hlkwd{exprs}\hlstd{(hlo[}\hlkwd{fData}\hlstd{(hlo)}\hlopt{$}\hlstd{markers} \hlopt{==} \hlstr{"Peroxisome"}\hlstd{, ])),}
         \hlkwc{lty} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"darkblue"}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"l"}\hlstd{)}
\hlkwd{legend}\hlstd{(}\hlstr{"topleft"}\hlstd{,} \hlkwd{c}\hlstd{(}\hlstr{"Mitochondrion"}\hlstd{,} \hlstr{"Peroxisome"}\hlstd{),}
       \hlkwc{lty} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"purple"}\hlstd{,} \hlstr{"blue"}\hlstd{),} \hlkwc{bty} \hlstd{=} \hlstr{"n"}\hlstd{)}
\end{alltt}
\end{kframe}
\includegraphics[width=.65\textwidth]{figure/plotDist-1}

@@

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Wed Nov  2 14:41:46 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127N &   1 & 127N & 1 to 6 (pooled) & 6.00 \\ 
  X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X128N &   1 & 128N & 10 to 11 (pooled) & 13.30 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
  X128N.1 &   2 & 128N & 10 to 11 (pooled) & 12.50 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

% On the figure below, we compare the relative intensities of channels 7
% to 10 on scatter plots, highlighting different marker sets. These
% differences result from different peak fractions for these niches on
% the mitochondrial and chromatin occupancy profiles for the two
% replicates.

% <<repl1, eval = TRUE, echo=FALSE, fig.width = 12>>=
% sel0 <- fData(hyperLOPIT)$markers != "unknown"
% cls <- paste0(getStockcol(), 80)[factor(fData(hyperLOPIT)$markers)]
% cls[!sel0] <- getUnknowncol()

% par(mfrow = c(2, 4))
% for (i in c(7, 8, 10, 9)) {
%     plot(exprs(hyperLOPIT[, c(i, i+10)]), col = cls,
%          main = paste("Channel", pData(hyperLOPIT)[i, "Fraction.No"]))
%     points(exprs(hyperLOPIT[sel0, c(i, i+10)]), col = cls[sel0], pch = 19)
%     grid()
%     abline(0, 1, col = "red")
% }
% plot(1:100, type = "n", xaxt = "n", yaxt = "n", xlab = "", bty = "n", ylab = "")
% addLegend(hyperLOPIT, fcol = "markers", where = "center", cex = .7)

% i <- fData(hyperLOPIT)$markers == "Mitochondrion"
% plotDist(hyperLOPIT[i, hyperLOPIT$Replicate == 2],
%          featureNames(hyperLOPIT)[i], type = "l",
%          mcol = "orange")
% title(main = "Mitochondrion")
% ## plotDist(hyperLOPIT[i, hyperLOPIT$Replicate == 2])
% matlines(t(exprs(hyperLOPIT[i, hyperLOPIT$Replicate == 1])), col = "#F781BF30", lty = 1)
% legend("topleft", paste("Replicate", 1:2),
%        col = c("#F781BF", "orange"),
%        lty = 1, bty = "n")

% i <- fData(hyperLOPIT)$markers == "Nucleus - Chromatin"
% plotDist(hyperLOPIT[i, hyperLOPIT$Replicate == 2],
%          featureNames(hyperLOPIT)[i], type = "l")
% ## plotDist(hyperLOPIT[i, hyperLOPIT$Replicate == 2])
% matlines(t(exprs(hyperLOPIT[i, hyperLOPIT$Replicate == 1])), col = "#984EA330", lty = 1)
% title(main = "Chromatin")
% legend("topleft", paste("Replicate", 1:2),
%        col = c("#984EA3", "steelblue"),
%        lty = 1, bty = "n")
% @

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{data}\hlstd{(hyperLOPIT2015ms3r1)}
\hlkwd{data}\hlstd{(hyperLOPIT2015ms3r2)}
\hlstd{mydata} \hlkwb{<-} \hlkwd{MSnSetList}\hlstd{(}\hlkwd{list}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2))}
\hlkwd{pRolocVis}\hlstd{(mydata,} \hlkwc{app} \hlstd{=} \hlstr{"compare"}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

The comparison app loads the two PCA plots side-by-side. Only common
proteins between the two data sets are displayed. As per the main
application proteins can be searched, identified and highlighted on
both PCA plots and in the dedicated profiles tab. One key feature of
the compare application is the ability to re-map the second dataset
onto the PCA data space of the first (reference) data set (see
\texttt{?pRolocVis} and the argument \texttt{remap = TRUE}). Using the first dataset
as the reference set, PCA is carried out on the first dataset and the
standard deviations of the principal components (i.e. the square roots
of the eigenvalues of the covariance/correlation matrix) and the
matrix of variable loadings (i.e. a matrix whose columns contain the
eigenvectors) are stored and then used to calculate the principal
components of the second dataset. Both datasets are scaled and
centered in the usual way. The first dataset appears on the left, and
the second re-mapped data appears on the right. The order of the first
(the reference data for remapping) and second dataset can be changed
through regeneration/re-ordering of the \texttt{MSnSetList} object.

The final application "classify", has been designed to view machine
learning classification results according to user-specified thresholds
for the assignment of proteins to its sub-cellular location, this is
discussed later in the subsection \textit{thresholding} in the
\textit{supervised machine learning section}.

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Wed Nov  2 14:41:46 2016 
## Added markers from  'pdres' marker vector. Wed Nov  2 14:41:46 2016 
##  MSnbase version: 1.99.7
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,}
                \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,}
                \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,}
                \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,}
                \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{)}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4348738               0.3025063               0.3885913 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6911470               0.6332177               0.4388085 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4206513               0.5959339               0.9495535 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7946359               0.7066474               0.3160929 
##         Plasma membrane              Proteasome 
##               0.7169909               0.4203854
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,}
                     \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,}
                     \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,}
                     \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,}
                     \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      85                     172                      87 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     301                     465                      96 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      26                     123                     523 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     230                     343                      39 
##         Plasma membrane              Proteasome                 unknown 
##                     330                     156                    2056
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Wed Nov  2 14:56:28 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Wed Nov  2 14:56:28 2016 
## Subset [6725,20][5032,20] Wed Nov  2 14:56:29 2016 
## Removed features with more than 0 NAs: Wed Nov  2 14:56:29 2016 
## Dropped featureData's levels Wed Nov  2 14:56:29 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hlo} \hlkwb{<-} \hlstd{hl[,} \hlkwd{order}\hlstd{(hl}\hlopt{$}\hlstd{Iodixonal.Density)]}
\hlkwd{plotDist}\hlstd{(hlo[}\hlkwd{fData}\hlstd{(hlo)}\hlopt{$}\hlstd{markers} \hlopt{==} \hlstr{"Mitochondrion"}\hlstd{, ],}
         \hlkwc{pcol} \hlstd{=} \hlstr{"purple"}\hlstd{,} \hlkwc{fractions} \hlstd{=} \hlstr{"Fraction.No"}\hlstd{)}
\hlkwd{title}\hlstd{(}\hlkwc{main} \hlstd{=} \hlstr{"Marker occupancy profiles along the gradient"}\hlstd{)}
\hlkwd{matlines}\hlstd{(}\hlkwd{t}\hlstd{(}\hlkwd{exprs}\hlstd{(hlo[}\hlkwd{fData}\hlstd{(hlo)}\hlopt{$}\hlstd{markers} \hlopt{==} \hlstr{"Peroxisome"}\hlstd{, ])),}
         \hlkwc{lty} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"darkblue"}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"l"}\hlstd{)}
\hlkwd{legend}\hlstd{(}\hlstr{"topleft"}\hlstd{,} \hlkwd{c}\hlstd{(}\hlstr{"Mitochondrion"}\hlstd{,} \hlstr{"Peroxisome"}\hlstd{),}
       \hlkwc{lty} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"purple"}\hlstd{,} \hlstr{"blue"}\hlstd{),} \hlkwc{bty} \hlstd{=} \hlstr{"n"}\hlstd{)}
\end{alltt}
\end{kframe}
\includegraphics[width=.6\textwidth]{figure/plotDist-1}

@@

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Wed Nov  2 14:56:30 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127N &   1 & 127N & 1 to 6 (pooled) & 6.00 \\ 
  X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X128N &   1 & 128N & 10 to 11 (pooled) & 13.30 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
  X128N.1 &   2 & 128N & 10 to 11 (pooled) & 12.50 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{data}\hlstd{(hyperLOPIT2015ms3r1)}
\hlkwd{data}\hlstd{(hyperLOPIT2015ms3r2)}
\hlstd{hllst} \hlkwb{<-} \hlkwd{MSnSetList}\hlstd{(}\hlkwd{list}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2))}
\hlkwd{pRolocVis}\hlstd{(hllst,} \hlkwc{app} \hlstd{=} \hlstr{"compare"}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

The comparison app loads the two PCA plots side-by-side. Only common
proteins between the two data sets are displayed. As per the main
application, proteins can be searched, identified and highlighted on
both PCA plots and in the dedicated profiles tab. One key feature of
the compare application is the ability to re-map the second dataset
onto the PCA data space of the first (reference) data set (see
\texttt{?pRolocVis} and the argument \texttt{remap = TRUE}). Using the first dataset
as the reference set, PCA is carried out on the first dataset and the
standard deviations of the principal components (i.e. the square roots
of the eigenvalues of the covariance/correlation matrix) and the
matrix of variable loadings (i.e. a matrix whose columns contain the
eigenvectors) are stored and then used to calculate the principal
components of the second dataset. Both datasets are scaled and
centered in the usual way. The first dataset appears on the left, and
the second re-mapped data appears on the right. The order of the first
(the reference data for remapping) and second dataset can be changed
through regeneration/re-ordering of the \texttt{MSnSetList} object.

The final application \textit{classify}, has been designed to view
machine learning classification results according to user-specified
thresholds for the assignment of proteins to its sub-cellular
location, this is discussed later in the subsection
\textit{thresholding} in the \textit{supervised machine learning
  section}.

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Wed Nov  2 14:56:30 2016 
## Added markers from  'pdres' marker vector. Wed Nov  2 14:56:31 2016 
##  MSnbase version: 1.99.7
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,}
                \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,}
                \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,}
                \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,}
                \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{)}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4332906               0.3032423               0.3840370 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6878996               0.5997368               0.4245347 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4291978               0.5892503               0.9494459 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7950790               0.7079212               0.3151288 
##         Plasma membrane              Proteasome 
##               0.7086233               0.4158484
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,}
                     \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,}
                     \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,}
                     \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,}
                     \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      85                     170                      88 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     297                     476                      93 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      27                     125                     523 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     230                     343                      38 
##         Plasma membrane              Proteasome                 unknown 
##                     321                     157                    2059
\end{verbatim}
\end{kframe}
\end{knitrout}
